KidsAIR: exposure model

### 2020-04-29 exposure_models.Rmd
multiple imputation updates

```{r}
library(mice)

# Select analysis vars
selected_vars <- analysis_data %>% 
  select(area, pm_mean_sampling_period, income_3level, residents_smoke, 
         stove_age_3level, home_windows_2level,
         chimney_clean_3level, wood_collect_2level,
         home_act_door, home_act_sweep, home_act_windows, 
         sums_events_sampling_period, mean_temp_sampling_period_5, 
         stove_grade_3level, moisture_closest_2level) %>% 
  mutate(home_act_door = factor(home_act_door, levels = c(0,1,2,3,4,5,6)),
         home_act_sweep = factor(home_act_sweep, levels = c(0,1,2,3,4,5,6)),
         home_act_windows = factor(home_act_windows, levels = c(0,1,2,3,4,5,6)),
         area = factor(area, levels = c("AK", "NN", "WMT")))

@@

# Look for patterns in missing data
md.pattern(selected_vars)

# Impute missing data; m = 20 datasets (check % missing data and match)
imputed_data <- mice(selected_vars, m=5,
                     method = c("polyreg", "pmm", "polr", "logreg", "polr",
                                "logreg", "polr", "logreg", "polr", "polr",
                                "polr", "pmm", "pmm", "polr", "logreg"))

summary(imputed_data)

@@

densityplot(selected_vars$pm_mean_sampling_period)

@@

@@

# Can do regression on the imputed data - either pooled or individual datasets

```

@@

# Using MAMI package, perform model averaging and selection
model_ave <- mami(imputed_data, missing.data = "imputed", model = "gaussian",
                  outcome = "pm_mean_sampling_period", 
                  method = "MA.criterion", criterion = "AIC", print.time = TRUE,
                  add.transformation = c("log(pm_mean_sampling_period)"))

                  #inference = "+boot", B = 2, X.org = selected_vars

>>>>

```{r}
library(mice)
library(pan)
library(multilevel)

# Select analysis vars
selected_vars <- analysis_data %>% 
  select(area, pm_mean_sampling_period, income_3level, residents_smoke, 
         stove_age_3level, home_windows_2level,
         chimney_clean_3level, wood_collect_2level,
         home_act_door, home_act_sweep, home_act_windows, 
         sums_events_sampling_period, mean_temp_sampling_period_5, 
         stove_grade_3level, moisture_closest_2level) %>% 
  mutate(home_act_door = factor(home_act_door, levels = c(0,1,2,3,4,5,6)),
         home_act_sweep = factor(home_act_sweep, levels = c(0,1,2,3,4,5,6)),
         home_act_windows = factor(home_act_windows, levels = c(0,1,2,3,4,5,6)),
         area = factor(area, levels = c("AK", "NN", "WMT")),
         log_pm_mean_sampling_period = log(pm_mean_sampling_period)) %>% 
  select(-pm_mean_sampling_period) %>% 
  filter(!is.na(income_3level) & !is.na(home_windows_2level))

# Look at structure of data and check variable types
str(selected_vars)

@@

# Look for patterns in missing data
missing_patterns <- md.pattern(selected_vars)

missing_patterns

sum(missing_patterns[, "residents_smoke"] == 0)

hist(selected_vars$pm_mean_sampling_period)

# Check for distribution between vars and missingness - see if there are patterns
## No obvious patterns in the missing data
## Missing covars do not seem to be related to the outcomes
missing_hist <- selected_vars %>% 
  mutate(missing_var = if_else(is.na(moisture_closest_2level), "missing yes", "missing no")) %>% 
  ggplot() +
    geom_bar(aes(log_pm_mean_sampling_period), color = "red") +
    facet_wrap(~missing_var)
missing_hist

# Check ICC 
multilevel::ICC1(aov(mean_temp_sampling_period_5 ~ area, data = selected_vars))

# Impute missing data; m = 20 datasets (check % missing data and match)
imputed_data <- mice(selected_vars, m=5, maxit = 5,
                     method = c("polyreg", "polr", "logreg", "polr",
                                "logreg", "polr", "logreg", "polr", "polr",
                                "polr", "pmm", "pmm", "polr", "logreg", "pmm"))

# Compare imputed summary to original summary
summary(selected_vars)
summary(complete(imputed_data))

# Look at imputation methods for each var; consider changing
imputed_data$method

@@

densityplot(selected_vars$log_pm_mean_sampling_period)

@@

# Print predictor matrix
## Keep considering, but I don't see a reason to alter this as of now
imputed_data$pred

@@

# Can do regression on the imputed data - either pooled or individual datasets
```

The above seems to be a good method of imputing the missing data, so moving on 
to model selection/averaging

@@

# Using MAMI package, perform model averaging and selection
## Will take ~20 to 30 mins with 5 iterations and bootstrap
model_ave <- mami(imputed_data, missing.data = "imputed", model = "gaussian",
                  outcome = "log_pm_mean_sampling_period", 
                  method = "MA.criterion", criterion = "AIC", print.time = TRUE,
                  inference = "+boot", B = 2, X.org = selected_vars)
